% -*- coding: utf-8 -*-
% Ada 95 品质和风格
% 版权所有 (C) 2009, 朱群英
% Copyright (C) 2009, Zhu Qun-Ying
%
% 本书的 TeX 代码和由之生成的 ps，pdf，html，等其他格式的文件
% 遵循 GNU通用公共授权第三版或其后的版本。
%
% 本书是基于有益的目的而加以发布，然而不负任何担保责任。
%
% 您应已收到附随于本书的GNU通用公共授权的副本；如果没有，
% 请参考 <http://www.gnu.org/licenses/gpl.html>

\chapter[英文原版的版权声明]{}
\pagestyle{empty}
\begin{center}
\textbf{\huge{Ada 95 Quality and Style:}}

\textbf{\large{Guidelines for Professional Programmers}}

\vfill
\textbf{\large{SPC-94-03-CMC}}

\vspace{2em}
\textbf{\large{Version 0.1.00.10}}

\vspace{2em}
\textbf{\large{October 1995}}

\vspace{2em}
\large{Prepared for\\
Department of Defense Ada Joint Program Office}

\vspace{2em}
Poduced by the\\
SOFTWARE PRODUCTIVITY CONSORTIU

\vspace{2em}
SPC Building

2214 Rock Hill Road

Herndon, Virginia 22070

\vspace{2em}

\end{center}

\vspace{2em}
\noindent
\footnotesize{
Copright \copyright{} 1995, \href{http://www.software.org}
{Software Productivity Consortium}, Herndon, Virginia.
This document can be copied and distributed without fee in the U.S., or
internationally. This is made possible under the terms of the DoD Ada Joint
Program Office's royalty-free, worldwide, non-exclusive, irrevocable license
for unlimited use of this material. This material is based in part upon work
sponsored by the DoD Ada Joint Program Office under
\href{http://www.arpa.mil/}{Advanced Research Projects
Agency} Grant \#MDA972-92-J-1018. The content does not necessarily reflect the position or the policy of the U.S. Government, and no official endorsement should
be inferred. The name Software Productivity Consortium shall not be used in
advertising or publicity pertaining to this material or otherwise without the
prior written permission of
\href{http://www.software.org}{Software Productivity Consortium, Inc}.
SOFTWARE PRODUCTIVITY CONSORTIUM, INC. MAKES NO REPRESENTATIONS OR WARRANTIES
ABOUT THE SUITABILITY OF THIS MATERIAL FOR ANY PURPOSE OR ABOUT ANY OTHER
MATTER, AND THIS MATERIAL IS PROVIDED WITHOUT EXPRESS OR IMPLIED WARRANTY OF
ANY KIND.}

${}${}
\vfill
\noindent
------------ ------------

\footnotesize{
\noindent
Ada-ASSURED is a trademark of \href{http://www.grammatech.com}{GrammaTech, Inc}.

\noindent
ADARTS  is a service mark of the
\href{http://www.software.org}{Software Productivity Consortium Limited}
Partnership.

\noindent
\href{http://www.ibm.com}{IBM} is a registered trademark of International
 Business Machines Corporation.

\noindent
VAX is a registered trademark of Digital Equipment Corporation.

\noindent
The X Window System is a trademark of the
\href{http://www.mit.edu}{Massachusetts Institute of Technology}.

\noindent
Other product names, or names of platforms referenced herein may be
trademarks or registered trademarks of their respective
companies, and they are used for identification purposes only.
}
